### 2012-11-25 paper.tex
added comparison tables

Using an unpruned tree doesn't improve the results:
\begin{lstlisting}
J48 unpruned tree
pericardial-effusion = 0
|   epss <= 13100: 1 (76.62/1.95)
|   epss > 13100
|   |   epss <= 15600: 0 (2.19/0.16)
|   |   epss > 15600: 1 (2.19/0.03)
pericardial-effusion = 1: 1 (14.0)
\end{lstlisting}
Here, the decision tree assumes a pericardial effusion (fluid around the heart) to be a healthy characteristic, but it is not. Accordingly, the precision of the J48 decreases from 95\% to 88\%. Using a higher confidence factor instead of a totally unpruned tree has no effect on the quality or the classification distribution.

\paragraph{Other parameter}
Neither the laplace correctin to smooth the count of the leaves nor reduced error pruning has any effect on the quality of result. Without mdl correction the precision decreases a little to 91.9\%. Raising the minimum of instances per leaf has no effect either, which is no suprise since the data set is rather small. We couldn't get a better result with the J48 algorithm than to classify all patients to survive at least one year. The detailed accuracy for this simple, single-sided classification can be seen in table
\ref{tab:echo:dec:best}.

\begin{table*}[htb]\centering
    \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
        \toprule 
        \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure &  Class  \\ \midrule
               &  0       & 0       & 0         & 0      & 0         &  0      \\     
               &  1       & 1       & 0.959     & 1      & 0.979     &  1      \\     
Weighted Avg.  &  0.959   & 0.959   & 0.919     & 0.959  & 0.939     &         \\ \bottomrule
    \end{tabular*}
\caption{Decision Tree -- best achievable results} 
\label{tab:echo:dec:best}
\end{table*}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  &Class\\
	\midrule
									&0         	&0         &0         	&0       &  0         & 0.5      &0\\
  								&1         	&1         &0.959     	&1       &0.979       &	0.5      &1\\

	Weighted Avg.		&0.959     	&0.959     &0.919   		&0.959   &0.939     	&0.5	&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &ROC Area  &Class\\
	\midrule
									&0         	&0         &0         &0       &  0         & 0.5      &0\\
  								&1         	&1         &0.959     &1       &0.979       &	0.5      &1\\

	Weighted Avg.		&0.959     	&0.959     &0.919   	&0.959   &0.939     	&0.5				&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the echocardiogram dataset}
\end{table}

@@

@@

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class \\   \midrule
               &  0.577   & 0.052   & 0.779     & 0.577  & 0.663     & >50K  \\   
               &  0.948   & 0.423   & 0.876     & 0.948  & 0.911     & <=50K \\   
Weighted Avg.  &  0.859   & 0.333   & 0.853     & 0.859  & 0.851     &       \\   \bottomrule
    \end{tabular*}
\caption{Random Forest -- 3 Random Features} 
\label{tab:adult:rand:3f}
\end{table*}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure &ROC Area  	&Class\\
	\midrule
									&0.568     	&0.062     &0.744     	&0.568   &0.644    	&0.753    	&	>50K\\
  								&0.938     	&0.432     &0.873     	&0.938   &0.904     &0.753    	&$\leq$50K\\

	Weighted Avg.   & 0.849    & 0.343     &0.842   		&0.849   &0.842     & 0.753			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the adult dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   &FP Rate   &Precision   &Recall  &F-Measure &ROC Area  	&Class\\
	\midrule
									&0.593     &0.088      &0.68      &0.593     &0.633    &0.884    		&>50K\\
									&0.912     &0.407      &0.876     &0.912     &0.893    &0.884    		&$\leq$50K\\

	Weighted Avg.   &0.835     &0.331      &0.829     &0.835     &0.831    &0.884 \\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the adult dataset}
\end{table}

@@

@@

\begin{table}[htb]
\centering
\begin{tabular}{llllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  	&Class\\ 
	\midrule
									&0.583     	&0.355     &0.55      	&0.583   &0.566   		&0.628    	&1\\
                 	&0.393     	&0.181     &0.389     	&0.393   &0.391      	&0.648    	&2\\
                 	&0.444     	&0.252     &0.484     	&0.444   &0.463      	&0.614    	&3\\
	Weighted Avg.   & 0.849    & 0.343      &0.842   &  0.849     &0.842     & 0.753			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the contraception dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &ROC Area  	&Class\\
	\midrule
									&0.569     	&0.351     &0.547     	&0.569   &0.558      	&0.65     	&1\\
                 	&0.414     	&0.166     &0.422     	&0.414   &0.418      	&0.677    	&2\\
                 	&0.438     	&0.279     &0.455     	&0.438   &0.447      	&0.603    	&3\\

	Weighted Avg.   &0.489     	&0.284     &0.487     	&0.489   &0.488      	&0.64			&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the contraception dataset}
\end{table}

@@

\bibliography{references}

>>>>

Using an unpruned tree doesn't improve the results:
\begin{lstlisting}
J48 unpruned tree
pericardial-effusion = 0
|   epss <= 13100: 1 (76.62/1.95)
|   epss > 13100
|   |   epss <= 15600: 0 (2.19/0.16)
|   |   epss > 15600: 1 (2.19/0.03)
pericardial-effusion = 1: 1 (14.0)
\end{lstlisting}
Here, the existence of a pericardial effusion (fluid around the heart) is assumed to be a healthy characteristic, but it is not. Accordingly, the precision of the J48 decreases from 95\% to 88\%.

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure   &Class\\
	\midrule
									&0         	&0         &0         	&0       &  0              &0\\
  								&1         	&1         &0.959     	&1       &0.979             &1\\

	Weighted Avg.		&0.959     	&0.959     &0.919   		&0.959   &0.939     		&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &Class\\
	\midrule
									&0         	&0         &0         &0       &  0         &0\\
  								&1         	&1         &0.959     &1       &0.979       &1\\

	Weighted Avg.		&0.959     	&0.959     &0.919   	&0.959   &0.939     					&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		\\
  Random Forest		\\
  Naive Bayes			&0.897  		& 0.244   	& 0.958   & 0.897  &0.92      	& \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939     	&	0.959\\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939     	&	0.959\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}

@@

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class \\   \midrule
               &  0.577   & 0.052   & 0.779     & 0.577  & 0.663     & >50K  \\   
               &  0.948   & 0.423   & 0.876     & 0.948  & 0.911     & $\leq$50K \\   
Weighted Avg.  &  0.859   & 0.333   & 0.853     & 0.859  & 0.851     &       \\   \bottomrule
    \end{tabular*}
\caption{Random Forest -- 3 Random Features} 
\label{tab:adult:rand:3f}
\end{table*}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure  	&Class\\
	\midrule
									&0.568     	&0.062     &0.744     	&0.568   &0.644    	    	&	>50K\\
  								&0.938     	&0.432     &0.873     	&0.938   &0.904         	&$\leq$50K\\

	Weighted Avg.   & 0.849    & 0.343     &0.842   		&0.849   &0.842     			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the adult dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   &FP Rate   &Precision   &Recall  &F-Measure &Class\\
	\midrule
									&0.593     &0.088      &0.68      &0.593     &0.633    &>50K\\
									&0.912     &0.407      &0.876     &0.912     &0.893    &$\leq$50K\\

	Weighted Avg.   &0.835     &0.331      &0.829     &0.835     &0.831     \\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the adult dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		&  0.846   	& 0.285   	& 0.843   & 0.846  &  0.844 		& FEHLT\\
  Random Forest		&  0.859   	& 0.333   	& 0.853   & 0.859  & 0.851     	& FEHLT\\
  Naive Bayes		 	&  0.83    	& 0.186   	& 0.854   & 0.83   & 0.837     	& FEHLT\\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     	& 0.849\\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831				& 0.835\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}

@@

\begin{table}[htb]
\centering
\begin{tabular}{lllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure     	&Class\\ 
	\midrule
									&0.583     	&0.355     &0.55      	&0.583   &0.566   		    	&1\\
                 	&0.393     	&0.181     &0.389     	&0.393   &0.391      	    	&2\\
                 	&0.444     	&0.252     &0.484     	&0.444   &0.463      	    	&3\\
	Weighted Avg.   & 0.849    & 0.343      &0.842   &  0.849     &0.842     			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the contraception dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure     	&Class\\
	\midrule
									&0.569     	&0.351     &0.547     	&0.569   &0.558      	     	&1\\
                 	&0.414     	&0.166     &0.422     	&0.414   &0.418      	    	&2\\
                 	&0.438     	&0.279     &0.455     	&0.438   &0.447      	    	&3\\

	Weighted Avg.   &0.489     	&0.284     &0.487     	&0.489   &0.488      				&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the contraception dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree 	&  0.558   & 0.243   & 0.557     	& 0.558  & 0.557     & FEHLT\\
  Random Forest		&  0.556   & 0.241   & 0.562     	& 0.556  & 0.556     & FEHLT\\
  Naive Bayes		 	&  0.508   & 0.243   & 0.528     	& 0.508  & 0.513     & FEHLT\\
  SVM							& 0.849    & 0.343   &0.842   		& 0.849  & 0.842 		 & 0.492\\
  kNN							&0.489     &0.284    &0.487     	& 0.489  & 0.488 		 & 0.489\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the contraceptive method choice dataset}
\end{table}
\bibliography{references}
